Zaca Fire Type Conversion

### 2020-09-20 Model Data Sheets and Code/Manuscript_Code.Rmd
added tuning code

>>>>

# Tuning Parameters

source: https://arxiv.org/pdf/1804.03515.pdf (see digital page 9 for tuneRanger)

replace: dataframe and response variable 
```{r}
set.seed(1127)

# run tuneRanger
mcf_task <- makeClassifTask(data = dataframe, target = "y variable")
tune_output <- tuneRanger(mcf_task, 
                          measure = list(mmce), 
                          num.trees = 1500, 
                          tune.parameters = c("mtry", "min.node.size"))

# get best parameter values
tune_output$model

```
get error when I try to add "replace" as a tuning parameter :(
